Toxic code snippets on Stack Overflow

### 2017-10-18 cloverflow-tse/cloverflow.tex
Incorporated Matheus's comments/changes.

%The popularity of the Internet encourages tremendous amount of source code being shared online. 
Stack Overflow is a popular online programming community with 7.6
million users, 14 million questions, and 23 million answers\footnote{Data as of 21
	August 2017 from~\url{https://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
to programming problems. The website has found to be useful for
software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also
valuable for educational purposes~\cite{Nasehi2012}. On Stack
Overflow, each conversation contains a question and a list of
answers. The answers frequently contain at least one code snippet as
a solution to the question asked. We found that the code snippets are
usually not authored directly on the Stack Overflow website but copied
from another location. A snippet in an answer could be copied and modified
from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS)
systems. The process of posting and answering questions on Stack
Overflow that involves reusing of source code, can be considered as
code cloning.

@@

We call code snippets that are copied from software systems to online
Q\&A websites (such as Stack Overflow) and vice versa as ``online
code clones''. There are two
directions in creating online code clones: (1) code is cloned from a software
project to a Q\&A website as an example; or (2) code is cloned from a
Q\&A website to a software project to obtain a functionality, perform
a particular task, or fixing a bug.
% and (3) code is transferred from one software project to another via a Q\&A website; 
Similar to classic clones, online code clones can lead to license
violations, bug propagation, introduction of vulnerabilities, and
re-use of outdated code. Unfortunately, online clones are 
difficult to locate and fix since the search space in online code
corpora is larger and no longer confined to a local repository.

Our survey of Stack Overflow answerers shows that online code cloning occurs on
Stack Overflow. Stack Overflow answerers frequently
clone code from other locations, such as their personal projects, company
projects, and open source projects, to Stack Overflow answers as a solution or
to complement their answer. The code cloning activity on Stack Overflow
is obviously beneficial considered the popularity of Stack Overflow and its
influence on software development~\FIXME{find citations}. On the other hand,
there is also a downside caused by low quality, defective, and harmful code
snippets that are reused without an awareness by millions of users.

One participants in our survey expresses his/her concerns about this:

@@

Toxic code snippets mean code snippets that are harmful for reuse and, in
several cases, are caused by online code cloning. Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1) outdated or (2) violating their original software license. Outdated code
can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license , e.g.~GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license and flow to other projects
with conflicting license, legal issues may occur.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2017-10-03) */
public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
  try {                                                 try {
    buffer.reset(b1,s1,l1); /* parse key1 */              buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                              key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */              buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                              key2.readFields(buffer);
  } catch (IOException e) {                               $$@buffer.reset(null,0,0); /* clean up reference */@
    throw new RuntimeException(e);                      } catch (IOException e) {
  }                                                       throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */         }
}                                                       return compare(key1, key2); /* compare them */
                                                      }
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{WritableComparator.java}}. The one from the
		Stack Overflow post 22315734 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). Its Apache v.2.0 license is also missing.}
	\label{fig:before-after}
\end{figure*}

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 801987 */             /* StringUtils.java (2017-10-03) */
public static String humanReadableInt(long number) {    public static String humanReadableInt(long number) {
  long absNumber = Math.abs(number);                      return TraditionalBinaryPrefix.long2String(number,"",1);
  double result = number;                               }
  String suffix = "";
  if (absNumber < 1024) {
  } else if (absNumber < 1024 * 1024) {
    result = number / 1024.0;
    suffix = "k";
  } else if (absNumber < 1024 * 1024 * 1024) {
    result = number / (1024.0 * 1024);
    suffix = "m";
  } else {
    result = number / (1024.0 * 1024 * 1024);
    suffix = "g";
  }
  return oneDecimal.format(result) + suffix;
}
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{StringUtils.java}}. The one from the
		Stack Overflow post 801987 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). The toxic code snippet is outdated code, has race conditions, and does not contain its
		original Apache v.2.0 license.}
	\label{fig:before-after_2}
\end{figure*}

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from {\small{\texttt{StringUtils}}} class in \textsf{hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{hadoop}. We can see that
they both are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
The missing of Apache v.2.0 license also similarly occurs after posted on 
Stack Overflow.

The two toxic code snippet in our examples has been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times as
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet in approximately every 5
days compared to almost every day for the second one. A quick web search shows
that the defective {\small{\texttt{humanReadableInt}}} method in the second
example already appears in approximately 500 projects on GitHub. Considering the
popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippets on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,302 online clones, at least 330 likely have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 154 of them, we found evidence that they have been copied
	from a specific Qualitas project and that 101 of them are meanwhile outdated. %
	% and questionable for being reused.

	\item \textbf{Awareness of Stack Overflow answerers to toxic code snippets:} We
	performed an online survey and collected answers from 201 highly-ranked Stack
	Overflow developers. We found that they cloned code snippets from open source
	projects to Stack Overflow answers. While Stack Overflow answerers are aware of
	their outdated code snippets, 19\% of the participants rarely
	or never fix the code. 99\% of the answerers never include software
	license in their snippets and 69\% never check for licensing conflicts between the
	cloned code snippets and Stack Overflow's CC BY-SA 3.0.

@@

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{itemize}
	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
		code cloned between Stack Overflow and open source projects?} We
	quantitatively measured the number of online code clones between Stack
	Overflow and open source projects to understand the scale of the
	problem. 
	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
		code clones occur?} We categorised online clones into seven
	categories allowing insights to why online code clones are created.
	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
		online code clones up-to-date compared to their counterparts in the
		original projects?} We were interested in the outdated Stack
	Overflow code examples since users are potentially reusing
	them. 
	\item \textbf{RQ4 (Software licensing violation): }\textit{Do
		licensing conflicts occur between Stack Overflow clones and their
		originals?} We investigated whether the reuse of online code clones
	can cause software developers to violate licenses.
	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }

	\textit{1) Do Stack Overflow
		answerers aware of the outdated code when
		they answer a question on Stack Overflow?}

	\textit{2) Do Stack Overflow
			answerers aware of licensing conflicts when
			they answer a question on Stack Overflow?}

@@

We rely on two source data sets in this study: Java code snippets in answers
on Stack Overflow and open source projects from the Qualitas corpus
\cite{QualitasCorpus}.

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in January 2016.
% The archived dump has a size of 9 gigabytes.
The data dump is in XML format containing information of posts (questions and
answers) and we were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006},
snippets of at least ten lines are usually more interesting since most of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode} methods are removed.
Each snippet was extracted from the dump and saved to a file. Moreover, we
filtered out irrelevant code snippets that were part of the accepted answers
but were not written in Java by using regular expressions and manual checking.
~\FIXME{@Jens, should I mention I use PMD CPD to help here? More confusing?}.
Finally we obtained
72,365 Java code snippets containing 1,840,581 lines\footnote{Measured by cloc:
	\url{https://github.com/AlDanial/cloc}} of Java source code. The median of the
snippet size is 17.

@@

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution due to lexical errors. iClones
could complete its execution but skipped 367 snippets due to malformed blocks in
Stack Overflow data sets. CCFinder reported 8 errors while processing the two data set. 
Although Simian, SourcererCC, and DECKARD
could successfully report clones, we decided to choose only Simian and
SourcererCC due to their fast detection speed.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2). \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Another benefit of SourcererCC is
its flexibility of detecting code clones between two systems.

We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the clone detection accuracy. Then, we deployed the
two detectors to locate clones between the two datasets.  For each Qualitas
project, we ran the tools on the project's code and the entire Stack Overflow
data. Due to incomplete code blocks and functions
normally found in Stack Overflow snippets, the built-in SourcererCC's Java
tokeniser could not parse 45,903 snippets, more than half of them. Nevertheless,
the tool provides an option to plug in a customised tokeniser, so we developed a
special Java tokeniser with assistance from the tool's creators. The customised
tokeniser successfully processed all Stack Overflow snippets.
Simian did not provide an option to detect cross-project clones. Hence the
Simian clone report was filtered to contain only clone pairs between Stack
Overflow and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas.

\begin{table}
	\centering
	\caption{Configurations of Simian and SourcererCC}
	\label{t:param_tuning}
%		\resizebox{\columnwidth}{!}{
%	\small
	\begin{tabular}{lp{5cm}}
		\toprule
		Tool & Configurations \\
		\midrule
		Simian~(\textit{S}) &  Threshold=10, ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers \\ 
		\midrule
		SourcererCC~(\textit{SCC}) & Functions, Minimum clone size=10, \newline Similarity=80\% \\
		\bottomrule
	\end{tabular} %
%	}
\end{table}

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators. All variable renaming are disabled to decrease a number of
false positives since we aim for finding clones that are copied from open source
projects with minimal modifications. The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statments (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\subsection{Phase 2: Clone Merging} Clones from the two detectors can be
duplicated. To avoid double-counting of the same clone pair, we adopted the idea
of \textbf{clone agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} to merge clones from two data
sets. Clone pairs agreed by both clone detection tools have a high
likelihood to be duplicate and must be merged. 
%By using this agreement-based
%approach, we reduced the number of clone candidates for manual investigation and
%avoid a threat to internal validity of double counting the same clone pair twice
%by merging the ones agreed by the two tools. 
To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching metric
proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large
enough number of overlapping lines can be categorised as either a good-match or
an ok-match pair with a
confidence value between 0 and 1. Although good-match has stronger agreement
than ok-match, we choose the ok-match criterion as our clone merging method
because it depends on clone containment and does
not take clone size into account. Clone containment suits our online code clones
from two tools, Simian (line-level) and SourcererCC (method-level), better
because Simian's clone fragments can be smaller or bigger than a method
while SourcererCC's clone fragments are always confined to a method boundary.

\ We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
fragments \textit{CF} is contained in each other:

@@

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We found one pair with
evidence of cloning from Stack Overflow post ID 698283 to
{\small\texttt{POIUtils.java}} in \textsf{jstock} project. The user
 who asked the question on Stack Overflow is an author of
\textsf{jstock}. The question is about determining the right method to call
among 7 overloading methods of {\small\texttt{setCellValue}} during runtime. We
could not find evidence of copying or attribution to Stack Overflow in
\textsf{jstock}. However, considering that the 25 lines of code of
{\small\texttt{findMethodToInvoke}} method depicted in \Cref{fig:jstock_code} in Stack
Overflow is very similar to the code in \textsf{jstock} including comments, it is almost certain that
the two code snippets form a clone pair. In addition, Stack Overflow answer was
posted on March 30, 2009, while the code in {\small\texttt{POIUtils}} class in
\textsf{jstock} was committed to GitHub on the next day of March 31, 2009.

@@

\subsubsection{Outdated Code Snippets} 
\vspace{0.25cm}
\textit{Do Stack Overflow
	answerers aware of the outdated code when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}

>>>>

%The popularity of the Internet encourages tremendous amount of source code being shared online. 
Stack Overflow is a popular online programming community with 7.6
million users, 14 million questions, and 23 million answers\footnote{Data as of 21
	August 2017 from~\url{https://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
to programming problems. The website has found to be useful for
software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also
valuable for educational purposes~\cite{Nasehi2012}. On Stack
Overflow, each conversation contains a question and a list of
answers. The answers frequently contain at least one code snippet as
a solution to the question asked. We found that the code snippets are
usually not authored directly on the Stack Overflow website but copied
from another location. A snippet in an answer could be copied and modified
from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS)
systems. The process of posting and answering questions on Stack
Overflow that involves the reuse of source code can be considered
code cloning.

@@

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones''.
There are two directions in creating online code clones: (1) code is cloned from
a software project to a Q\&A website as an example; or (2) code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3) code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.~clones between software systems, online code clones
can lead to license violations, bug propagation, introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.

Our survey of Stack Overflow answerers shows that online code cloning occurs on
Stack Overflow. Stack Overflow answerers frequently
clone code from other locations, such as their personal projects, company
projects, and open source projects, to Stack Overflow as a solution or
a complement to a solution. The code cloning activity on Stack Overflow
is obviously beneficial considered the popularity of Stack Overflow and its
influence on software development~\FIXME{find citations}. On the other hand,
there is also a downside caused by low quality, defective, and harmful code
snippets that are reused without an awareness by millions of users.

One participant in our survey expresses his/her concerns about this:

@@

Toxic code snippets mean code snippets that are harmful for reuse and, in
several cases, are caused by online code cloning. Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1) outdated or (2) violating their original software license. Outdated code
can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license , e.g.~GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting license, legal issues may occur.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2014-11-21) */
public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
  try {                                                 try {
    buffer.reset(b1,s1,l1); /* parse key1 */              buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                              key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */              buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                              key2.readFields(buffer);
  } catch (IOException e) {                               $$@buffer.reset(null,0,0); /* clean up reference */@
    throw new RuntimeException(e);                      } catch (IOException e) {
  }                                                       throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */         }
}                                                       return compare(key1, key2); /* compare them */
                                                      }
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{WritableComparator.java}}. The one from the
		Stack Overflow post 22315734 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). Its Apache v.2.0 license is also missing.}
	\label{fig:before-after}
\end{figure*}

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow post ID 801987 */             /* StringUtils.java (2013-02-05) */
public static String humanReadableInt(long number) {    public static String humanReadableInt(long number) {
  long absNumber = Math.abs(number);                      return TraditionalBinaryPrefix.long2String(number,"",1);
  double result = number;                               }
  String suffix = "";
  if (absNumber < 1024) {
  } else if (absNumber < 1024 * 1024) {
    result = number / 1024.0;
    suffix = "k";
  } else if (absNumber < 1024 * 1024 * 1024) {
    result = number / (1024.0 * 1024);
    suffix = "m";
  } else {
    result = number / (1024.0 * 1024 * 1024);
    suffix = "g";
  }
  return oneDecimal.format(result) + suffix;
}
	\end{lstlisting}\vspace{-2ex}
	\caption{An example of the two code fragments of
		{\small\texttt{StringUtils.java}}. The one from the
		Stack Overflow post 801987 (left) is outdated when compared to
		its latest version in the \textsf{hadoop} code base
		(right). The toxic code snippet is outdated code, has race conditions, and does not contain its
		original Apache v.2.0 license.}
	\label{fig:before-after_2}
\end{figure*}

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{hadoop}. We can see that
they are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
The absence of Apache v.2.0 license also occurs after the snippet is posted on 
Stack Overflow.

The two toxic code snippet in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times as
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet in approximately every 5
days compared to almost every day for the second one. A quick web search shows
that the defective {\small{\texttt{humanReadableInt}}} method in the second
example already appears in approximately 500 projects on GitHub. Considering the
popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippets on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,302 online clones, at least 330 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 154 of them, we found evidence that they have been copied
	from a specific open source project and that 101 of them are outdated. %
	% and questionable for being reused.

	\item \textbf{Awareness of Stack Overflow answerers to toxic code snippets:} We
	performed an online survey and collected answers from 201 highly-ranked Stack
	Overflow users. We found that they cloned code snippets from open source
	projects to Stack Overflow answers. While Stack Overflow answerers are aware of
	their outdated code snippets, 19\% of the participants rarely
	or never fix the code. 99\% of the answerers never include software
	license in their snippets and 69\% never check for licensing conflicts between the
	cloned code snippets and Stack Overflow's CC BY-SA 3.0.

@@

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{itemize}
	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
		code cloned between Stack Overflow and open source projects?} We
	quantitatively measured the number of online code clones between Stack
	Overflow and open source projects to understand the scale of the
	problem. 
	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
		code clones occur?} We categorised online clones into seven
	categories allowing insights to why online code clones are created.
	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
		online code clones up-to-date compared to their counterparts in the
		original projects?} We were interested in the outdated Stack
	Overflow code examples since users are potentially reusing
	them. 
	\item \textbf{RQ4 (Software licensing violation): }\textit{How often do
		licensing conflicts occur between Stack Overflow clones and their
		originals?} We investigated whether the reuse of online code clones
	can cause software developers to violate licenses.
	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }

	\textit{1) How often are Stack Overflow
		answerers aware of the outdated code when
		they answer a question on Stack Overflow?}

	\textit{2) How often are Stack Overflow
			answerers aware of licensing conflicts when
			they answer a question on Stack Overflow?}

@@

We rely on two source code data sets in this study: Java code snippets in answers
on Stack Overflow and open source projects from the Qualitas corpus
\cite{QualitasCorpus}, as detailed next.

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in January 2016.
% The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information of posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006},
we empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode} methods,
which are not interesting for the study.
Each snippet was extracted from the dump and saved to a file. Moreover, we
filtered out irrelevant code snippets that were part of the accepted answers
but were not written in Java by using regular expressions and manual checking.
~\FIXME{@Jens, should I mention I use PMD CPD to help here? More confusing?}.
Finally we obtained
72,365 Java code snippets containing 1,840,581 lines\footnote{Measured by cloc:
	\url{https://github.com/AlDanial/cloc}} of Java source code. The median size of the
snippet is 17 lines.

@@

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to the nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution due to lexical errors. iClones
could complete its execution but skipped 367 snippets due to malformed blocks in
Stack Overflow data sets. CCFinder reported 8 errors while processing the two data set. 
Although Simian, SourcererCC, and DECKARD
could successfully report clones, we decided to choose only Simian and
SourcererCC due to their fast detection speed.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2)~\cite{Bellon2007}. \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}.

We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the clone detection accuracy. Then, we deployed the
two detectors to locate clones between the two datasets.  For each Qualitas
project, we ran the tools on the project's code and the entire Stack Overflow
data. Due to incomplete code blocks and functions
normally found in Stack Overflow snippets, the built-in SourcererCC's Java
tokeniser could not parse 45,903 snippets, more than half of them. Nevertheless,
the tool provides an option to plug in a customised tokeniser, so we developed a
special Java tokeniser with assistance from the tool's creators. The customised
tokeniser successfully processed all Stack Overflow snippets.

Simian did not provide an option to detect cross-project clones. Hence the
Simian clone report was filtered to contain only clone pairs between Stack
Overflow and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas. 
SourcererCC can detect cross-project clones between two systems so we did
not filter the clones.

\begin{table}
	\centering
	\caption{Configurations of Simian and SourcererCC}
	\label{tab:clone_config}
%		\resizebox{\columnwidth}{!}{
%	\small
	\begin{tabular}{lp{5cm}}
		\toprule
		Tool & Configurations \\
		\midrule
		Simian~(\textit{S}) &  Threshold=10, ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers \\ 
		\midrule
		SourcererCC~(\textit{SCC}) & Functions, Minimum clone size=10, \newline Similarity=80\% \\
		\bottomrule
	\end{tabular} %
%	}
\end{table}

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. All variable renaming are disabled to decrease the number of
false positives since we aim for finding clones that are copied from open source
projects with minimal modifications. The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statments (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\subsection{Phase 2: Clone Merging} Clones from the two detectors can be
duplicated. To avoid double-counting of the same clone pair, we adopted the idea
of \textbf{clone agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} to merge clones from two data
sets. Clone pairs agreed by both clone detection tools have a high
likelihood to be duplicate and must be merged. 
%By using this agreement-based
%approach, we reduced the number of clone candidates for manual investigation and
%avoid a threat to internal validity of double counting the same clone pair twice
%by merging the ones agreed by the two tools. 
To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching metric
proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs that have a large
enough number of overlapping lines can be categorised as either a good-match or
an ok-match pair with a
confidence value between 0 and 1. Although good-match has stronger agreement
than ok-match, we choose the ok-match criterion as our clone merging method
because it depends on clone containment and does
not take clone size into account. Clone containment suits our online code clones
from two tools, Simian (line-level) and SourcererCC (method-level), better
because Simian's clone fragments can be smaller or bigger than a method
while SourcererCC's clone fragments are always confined to a method boundary.

\ We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
fragments \textit{CF} are contained in each other:

@@

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We found one pair with
evidence of cloning from Stack Overflow post ID 698283 to
{\small\texttt{POIUtils.java}} in \textsf{jstock} project. The user
 who asked the question on Stack Overflow is an author of
\textsf{jstock}. The question is about determining the right method to call
among 7 overloading methods of {\small\texttt{setCellValue}} during runtime. We
could not find evidence of copying or attribution to Stack Overflow in
\textsf{jstock}. However, considering that the 25 lines of code of
{\small\texttt{findMethodToInvoke}} method depicted in \Cref{fig:jstock_code} in Stack
Overflow is very similar to the code in \textsf{jstock} including comments, it is almost certain that
the two code snippets form a clone pair. In addition, the Stack Overflow answer was
posted on March 30, 2009, while the code in {\small\texttt{POIUtils}} class in
\textsf{jstock} was committed to GitHub on the next day of March 31, 2009.

@@

\subsubsection{Outdated Code Snippets} 
\vspace{0.25cm}
\textit{How often are Stack Overflow
	answerers aware of the outdated code when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}
